Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
adding preliminary shotplans

\documentclass[10pt, compress, draft]{beamer}
\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

@@

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item \underline{We must prioritize}
		\item

	\end{itemize}
\end{frame}

\begin{frame}{Focal points}
	Hmode (Proponentrs)
	L-mode :  neutrals Ip scan
\end{frame}

\begin{frame}{requirements form cross machine comparison }
same configuration, SN Btimes grad b, cryo pumps, greenwald fraction, heating

things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,

same diagnostics Isat blob speed, density profiles (Libes reflectometry), , divertor n and Te, fast camera plus n and te measure at OM

status of cameras on devices

@@

\begin{frame}{Proposed shot plan}
	piggybaggers (Mclements, relfectometry guys)

@@

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

@@

\section{Topic 21 experiments }
\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
	\begin{itemize}
		\item 15 proposals submitted to Topic 21
		\item Proposals include experiments on all three machines 
		\item There are overlaps between several of the proposals 
		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
		\item However, total number of proposed shots:  \textbf{449}
		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
	\end{itemize}
\end{frame}

\begin{frame}{Focal points}
\begin{itemize}
	\item MST1 uniquely facilitates cross comparison between machines
	\item Several of the proposed experiments overlap 
	\item A cross machine experiment has the makings of settling open issues
	\item Therefore, we will allocate shots for cross-machine comparison
	\item L-mode experiments: 
	\begin{enumerate}
		\item Investigate the role of neutrals 
		\item $I_p$ and $q_{95}$ scans
	\end{enumerate}
	\item H-mode experiments. 
\end{itemize}	
\end{frame}

\begin{frame}{L-mode experiments}
	\begin{itemize}
		\item The role of neutrals in the shoulder formation is not understood 		{\scriptsize(proponents: Carralero, Militello, Vianello, Walkden)}
		\begin{enumerate}
			\item We envisage to measure neutral gas profiles at the outboard 		midplane using fast cameras and reciprocating Langmuir probes
			\item Reciprocating probes and fast cameras available on all machines
		\end{enumerate}
		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$. {\scriptsize(proponents: Carralero, Militello, Vianello, Tsui, Walkden)}
		\begin{enumerate}
			\item Carry out parameter scans on all machines
			\item Strive after similar machine configurations
		\end{enumerate}
	\end{itemize}
\end{frame}

\begin{frame}{H-mode experiments}
\begin{itemize}
	\item ITER and DEMO will operate in H-mode
	\item We must know what parameters control shoulder formation 
	\item Shoulder formation parameter regime is unclear on all machines
	\item Main priorities: 
	\begin{enumerate}
		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
		\item Experiments must gradually increase power and density. 
	\end{enumerate}
\end{itemize}

@@

\begin{frame}{Optimizing cross machine comparison}
\begin{itemize}
	\item Machines are fundamentally differently designed
	\item Strive for similar configurations of the machines:
	\begin{enumerate} 
		\item Single-Null
		\item $\bm{B} \times \nabla B$ towards active divertor 
		\item Strike-point and cryo pump location (AUG and MAST-U)
		\item Heating 
	\end{enumerate}
\end{itemize} 
%things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,

\begin{frame}{Required diagnostics}
In order to compare experiments the following diagnostics must be available: 
\begin{enumerate}
	\item Reciprocating probe at OM measuring: 
	\begin{itemize} 
		\item $I_sat$ on minimum three pins poloidally and radially separated
		 (filamens speed and size). 
		\item Electron temperature
		\item If possible $M_{\|}$
	 \end{itemize}
	 \item Camera viewing OM for measuring neutrals 
	 \item Divertor measurements of $n$ and $T_e$ (probes). Collisionallity
	 \item Density profile measurements (Li-Bes, Reflectometry, Edge Thomson scattering) 
%	\item H-mode quality diagnostics(div current, magnetics)
\end{enumerate}
\end{frame}

\begin{frame}{Proposed shot plan - AUG}
Allocated shots $\sim$ 14 + contingency 
\begin{itemize}
	\item L-Mode (6 shots)
	\begin{enumerate}
		\item 
	\end{enumerate}
\end{itemize}

Choose fueling levels for reference shot at 0.8 MA from AUG14-2.2-3 30276. Perform the same density ramp at 0.6 MA by keeping the same Toroidal Field
Repeat Shot  1 by keeping the same q95 as reference
Repeat Shot  30276 @ 1MA with the same toroidal field
Repeat  3 by keeping the same q95 as the reference
Repeat  30276 with Reverse Bt
Repeat  5 with Probe at different insertion
H-Mode investigation: Foreseen number 9

The reference shot is 33059 (AUG15-2.2-3) with the aim to reach the condition found in 31607 (Sun PPCF 2015)

Scenario development. Start from succesful shot 33059 (Total heating 3.1 MW), keep the probe head in a safe position (FAR SOL) increase the heating power (two steps to 4.5 and 6) up to 6 MW monitoring midplane probe by IR and Divertor through Langmuir.
Repeat  1 Fueling ramps according to reference. Monitor of Divertor condition
Repeat  2 adjusting eventually the fueling and N seeding ramp monitoring the Divertor condition
Repeat  4 with optimum level of Fueling/Seeding 1st Radial position of probe
Repeat  5, different probe position
Repeat  6, different probe position
Repeat  6 with Strike-point sweeping (if feasible)
Contingency
Contingency

	piggybaggers (Mclements, relfectometry guys)

@@

	Decisions made here uploaded to wiki
